Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-06-10 paper/v2/paper.tex
small wording changes

To reduce configuration errors, many practitioners have a adopted a template-based
approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%
While templates help ensure certain kinds of consistency across devices,
they do not provide fundamentally different abstractions from existing configuration languages
or bridge the semantic divide between network-wide policies and device-level configuration.
%They do not provide fundamentally different abstractions
%from existing configuration languages and
Thus, they still require operators to
manually decompose policies into device behaviors.

@@

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{In this paper we assume that BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

@@

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address space in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.

>>>>

To reduce configuration errors, many practitioners have adopted a template-based
approach~\cite{hatch,thwack}, in which common tasks are captured as parameterized templates.
%
%More powerful still are systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure}, which use SAT solving
%and model finding tools to fill in parameters in configurations while
%ensuring key correctness constraints are satisfied.
%One step further, systems like
%ConfigAssure~\cite{narain:lisa05,narain+:configassure} use SAT solving
%and model finding tools to correctly and consistently fill in some parameters.
%
While templates help ensure certain kinds of consistency across devices,
they do not provide fundamentally different abstractions from existing configuration languages
or bridge the semantic divide between network-wide policies and device-level configuration.
%They do not provide fundamentally different abstractions
%from existing configuration languages and
Thus, they still require operators to
manually decompose policies into device behaviors.

@@

The BGP configurations produced by our compiler are
guaranteed to be policy-compliant in the face of
{\em arbitrary} failures.\footnote{In this paper we assume that either BGP is the only control plane protocol running in the network or the other protocols are correctly configured and do not have adverse interactions with BGP~\cite{igp-correctness1,igp-correctness2}.} This does not mean that the implementation is always
able to send traffic to its ultimate destination
(\EG in the case of a network partition), but rather that it always respects the
centralized policy, which may include dropping traffic when there is no route.
%
In this way, we provide network operators
with a strong guarantee that is otherwise impossible to achieve
today.
However, some policies simply cannot be implemented correctly in BGP in
 the presence of arbitrary failures.  We develop new
algorithms to detect such policies
and report our findings to the operators, so they may fix the policy
specification at compile time rather than experience undesirable
behavior after the configurations are deployed.
%We also analyze route aggregation to detect the possibility of failure-induced black-holes.

@@

 While configuring policies for a fully functional network is difficult, ensuring policy compliance in the face of failures can be almost impossible. Consider the data center network in Figure~\ref{fig:example2} with routers organized as a fat tree and running BGP.\footnote{For scale and policy flexibility, data center networks increasingly use BGP internally, with a private AS number per router~\cite{bgp-in-dc}.} The network has two clusters, one with services that should be reachable globally and one with services that should be accessible only internally. This policy is enabled by using non-overlapping address spaces in the two clusters and ensuring that only the address space for the global services is announced externally. Further, to reduce the number of prefixes that are announced externally, the global space is aggregated into a less-specific prefix \CD{PG}. The semantics of aggregation is that the aggregate prefix is announced as long as the router has a path to at least one sub-prefix.
